%------------------------
% Aditya Singh Bakawat - ATS Optimized Resume
%------------------------
\documentclass[a4paper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[pdftex]{hyperref}
\usepackage{fontawesome5}
\usepackage{fancyhdr}
% Hyperlink color
\hypersetup{
  colorlinks=true,
  urlcolor=RoyalBlue
}

% Page style
\pagestyle{fancy}
\fancyhf{} % clear header & footer
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins adjustments
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.45in}
\addtolength{\textheight}{1in}

% Appearance
\urlstyle{rm}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Slightly tighter spacing
\linespread{0.98}

% Section formatting
\titleformat{\section}{
  \scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule]
\titlespacing*{\section}{0pt}{4pt}{4pt}

%-------------------------
% Custom commands
%-------------------------
\newcommand{\resumeItem}[2]{
  \item\small{\textbf{#1:} #2 \vspace{-3pt}}
}
\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{#1 \vspace{-3pt}}
}

% Improved/robust subheading (left column wider so long course lines fit better)
\newcommand{\resumeSubheading}[4]{%
  \item
  \begin{minipage}[t]{0.66\linewidth}% Left column (slightly wider)
    \textbf{#1}\\[2pt]%
    \textit{#3}%
  \end{minipage}%
  \hfill % Separator
  \begin{minipage}[t]{0.32\linewidth}% Right column
    \raggedleft #2 \\[2pt] \textit{#4}% % Made #4 italic for consistency
  \end{minipage}%
  \vspace{-6pt}%
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{1pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=1.5em, label=\textbullet]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
% Document begins
%-----------------------------
\begin{document}

%---------- HEADING (ATS-friendly) -----------------
\begin{center}
	  \vspace{-45pt}
	  {\Huge \scshape Aditya Singh Bakawat} \\[2pt]
	  Jaipur, India \\[3pt]
	  \small
	  \raisebox{-0.1\height}\faPhone\ +91 8306454179 \quad
	  \href{mailto:24uec244@lnmiit.ac.in}{\raisebox{-0.2\height}\faEnvelope\ \underline{24uec244@lnmiit.ac.in}} \quad
	  \href{https://www.linkedin.com/in/aditya-singh-bakawat-5015a9323//}{\raisebox{-0.2\height}\faLinkedin\ \underline{LinkedIn}} \\
	  \href{https://github.com/CyberKun}{\raisebox{-0.2\height}\faGithub\ \underline{GitHub}} \quad
	  \href{https://codeforces.com/profile/Bruten}{\raisebox{-0.2\height}\faLink\ \underline{Codeforces}} \quad
	  \href{https://leetcode.com/u/Onee_Chan/}{\raisebox{-0.2\height}\faLink\ \underline{LeetCode}} \quad
	  \href{https://www.codechef.com/users/main_noble_29}{\raisebox{-0.2\height}\faLink\ \underline{CodeChef}}
\end{center}
\vspace{-18pt}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The LNM Institute of Information Technology}{Jaipur, India}
      {Bachelor of Technology - Electronics And Communication Engineering; CGPA: \textbf{8.53}}{July 2024 -- June 2028}
    
    % --- FIX: Courses list moved out of the command and placed in its own item ---
    \item[] \vspace{2pt} % Creates a new, full-width item with no bullet
    %{\scriptsize \textit{Courses:} Object-Oriented Programming, Data Structures and Algorithms, Design and Analysis of Algorithms, Python Programming, Database Management Systems, Computer Organization and Architecture, Operating Systems, Computer Networks}
   % Adds a bit of space before the next school
    % --- End Fix ---
     \vspace{-4pt}
    \resumeSubheading
      {Sanskar School}{Jaipur, India}
      {Class 12\textsuperscript{th} - Percentage: \textbf{85.6\%}}{Completed: March 2023}

    \resumeSubheading
      {Sanskar School}{Jaipur, India}
      {Class 10\textsuperscript{th} - Percentage: \textbf{95.0\%}}{Completed: March 2021}
  \resumeSubHeadingListEnd
%----------- PROJECTS -----------------
\section{Projects}
\resumeSubHeadingListStart
  %----------- NEW PROJECT: WorldWay-Express -----------------
\resumeSubheading
  {WorldWay-Express (Travel Route Optimizer)}
  {} % You can change this to "Personal Project" or leave empty
  {}{} 
\resumeItemListStart
  \vspace{-11pt}
  \resumeItem{Core Logic}{Architected a travel planner using \textbf{Dijkstra’s Algorithm} to calculate the most efficient routes across multi-modal transport systems (bus and plane).}
  \resumeItem{Optimization}{Designed a weighted graph representing various transit nodes, optimizing for travel time and distance across complex transport networks.}
  \resumeItem{Implementation}{Developed the backend in \textbf{C++} leveraging the Standard Template Library (STL) for high-performance priority queue management and graph traversal.}
  \resumeItem{Tech Stack}{C++, Data Structures (Graphs), Algorithms (Dijkstra's), STL}
\resumeItemListEnd
\resumeSubHeadingListEnd
       \vspace{-5pt}
%----------- SKILLS -----------------
\section{Skills}
\resumeSubHeadingListStart
  \resumeSubItem{Programming Languages}{C++, C, Python, Java, JavaScript, SQL, Bash}
  \resumeSubItem{Web Development}{React.js, Node.js, Express.js, Three.js, Flask, HTML, CSS}
  \resumeSubItem{Databases}{MySQL, MongoDB, PostgreSQL}
  \resumeSubItem{Libraries/Frameworks}{NumPy, Pandas, OpenCV, Pybind11}
  \resumeSubItem{Tools \& Platforms}{Git, Linux, Windows, VS Code, Google Colab, CMake, Docker}
% --- CHANGED --- Removed "Soft Skills" line. This directly addresses the "Buzzwords" and "Skills section" feedback.
\resumeSubHeadingListEnd

%----------- EXPERIENCE -----------------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Cybros — LNMIIT}{Jaipur, India}
    {Problem Setter \& Tester}{Aug 2025 -- Present}
  \resumeItemListStart
    \resumeItem{Problem Setting}{Created \textbf{20+ original problems} on \textbf{Codeforces (Polygon)} to engage and challenge beginner-level participants.}
    \resumeItem{Testing Validation}{Verified \textbf{50+ peer-authored problems} for logic, correctness, and difficulty balance.}
    \resumeItem{Mentorship}{Mentored \textbf{100+ peers} via live sessions focused on algorithmic techniques and contest preparation.}
 \vspace{-12pt}
% --- CHANGED --- Reworded to be more specific and results-oriented, removing the vague "enhancing coding culture".
    \resumeItem{Event Management}{Led and managed end-to-end programming contests and Hackathons for \textbf{200+ participants}, coordinating problem sets and event logistics.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%----------- HONORS AND AWARDS -----------------
\section{Honors and Awards}
\resumeItemListStart
  \resumeItemWithoutTitle{\textbf{Specialist} on \href{https://codeforces.com/profile/roronoa_2z}{Codeforces} with a peak rating of \textbf{1427}, placing among the top competitive programmers globally.}
  
  \resumeItemWithoutTitle{Achieved \textbf{Global Rank 1477} in \href{https://codeforces.com/contest/2126}{Codeforces Round 1037 (Div. 3)} and \textbf{Global Rank 1904} in \href{https://codeforces.com/contest/2160}{Codeforces Round 1058 (Div. 2)}, competing against thousands of participants worldwide.}
  
  \resumeItemWithoutTitle{Solved more than \textbf{500+ algorithmic and data structure problems} across platforms including Codeforces, CSES, and other competitive programming judges, demonstrating consistency and problem-solving depth.}
  
  \resumeItemWithoutTitle{Secured \textbf{3\textsuperscript{rd} rank out of 187} students in the Y-24 Electronics and Communication Engineering batch at LNMIIT, based on cumulative academic performance.}
\resumeItemListEnd


%----------- EXTRACURRICULAR -----------------
\section{Extracurricular}
\resumeSubHeadingListStart
  \resumeSubItem{Football}{Secured \textbf{3\textsuperscript{rd} place} in a \textbf{District-Level Football Tournament}, competing against multiple teams and demonstrating teamwork, endurance, and match discipline.}
  
  \resumeSubItem{Cricket}{Represented the \textbf{school cricket team} in \textbf{20+ competitive matches}, contributing to strategic field placements, on-field coordination, and overall team performance.}
\resumeSubHeadingListEnd


\end{document}